### 2024-11-23 paper/background.tex
Add red mark for change

% Structured Control Flow
Wasm supports control instructions for structured control flow, which
eliminates the need for arbitrary jumps, ensuring structured and predictable
execution.
Control instructions include \texttt{blocks}, \texttt{call}, \texttt{br}, and
\texttt{return}, which are explicitly delimited in the code.
Each control instruction is associated with \textit{contexts} that facilitate
structured execution and aid in handling nested or complex control flows.
For instance, the \texttt{block} instruction groups a sequence of instructions
and provides a scoped execution context with a \textit{label}, while the
\texttt{call} instruction executes body of a function with a \textit{frame}.
The \texttt{br} and \texttt{return} instructions jumps to the beginning or
the end of the block and the function, specified within the contexts, providing
targeted control transfers.

>>>>

% Structured Control Flow
\red{Wasm supports control instructions for structured control flow, which
eliminates the need for arbitrary jumps, ensuring structured and predictable
execution.
Control instructions include \texttt{blocks}, \texttt{call}, \texttt{br}, and
\texttt{return}, which are explicitly delimited in the code.
Each control instruction is associated with \textit{contexts} that facilitate
structured execution and aid in handling nested or complex control flows.
For instance, the \texttt{block} instruction groups a sequence of instructions
and provides a scoped execution context with a \textit{label}, while the
\texttt{call} instruction executes body of a function with a \textit{frame}.
The \texttt{br} and \texttt{return} instructions jump to the beginning or
the end of the block and the function, specified within the contexts, providing
targeted control transfers.
}
